---
title: "UC Career Tracks Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---
```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(scales)
library(DT)
library(hrbrthemes)

```

```{r global, include = FALSE}
career_tracks <- readRDS("career_tracks.RDS")

normal_prob_area_plot <- function(lb, ub, mean = 0, sd = 1, limits = c(mean - 3 * sd, mean + 3 * sd)) {
  x <- seq(limits[1], limits[2], length.out = 100)
  xmin <- max(lb, limits[1])
  xmax <- min(ub, limits[2])
  areax <- seq(xmin, xmax, length.out = 100)
  area <- data.frame(x = areax, ymin = 0, ymax = dnorm(areax, mean = mean, sd = sd))
  (ggplot()
    + geom_line(data.frame(x = x, y = dnorm(x, mean = mean, sd = sd)),
                mapping = aes(x = x, y = y))
    + geom_ribbon(data = area, mapping = aes(x = x, ymin = ymin, ymax = ymax))
    + scale_x_continuous(limits = limits))
}

perc_rank <- function(x) trunc(rank(x))/length(x)

```

Sidebar {.sidebar data-width=300}
=======================================================================

### Family and Functions

```{r}
selectInput("jfamily", "Select your Job Family:", unique(career_tracks$job_family))
uiOutput('ui_function')
uiOutput('ui_title')
numericInput("emp_salary", "Enter your annual salary:", 68500, 0, 300000)
actionButton("button", "Submit")

output$ui_function <- renderUI({
       jfunctions <- career_tracks %>% 
         filter(job_family == input$jfamily) %>% 
         .$job_function %>% 
         unique()
      selectInput('jfunction', 'Select your Job Function:', jfunctions)
})

output$ui_title <- renderUI({
  jtitles <- career_tracks %>% 
    filter(job_family == input$jfamily,
           job_function == input$jfunction) %>% 
    .$official_title %>% 
    unique()
  selectInput('jtitle', "Select your Job Title:", jtitles)
})
  
```

Use the **Career Tracks Summaries** tab to locate your UC Career Tracks family, function, and title. Then, enter
your annual salary and click "Submit" to calculate your compensation percentile. 

Use the **Other Information** tab to browse miscellaneous charts pertaining to UC Career Trackks.

***

More information can be found at the [UC Career Tracks website.](http://ucnet.universityofcalifornia.edu/working-at-uc/your-career/career-tracks/index.html)

Career Tracks Summaries
=======================================================================

Row
-----------------------------------------------------------------------

### Job Families and Functions

```{r}
dataTableOutput("job_table")
output$job_table <- renderDataTable(
  career_tracks %>% 
  select(Family = job_family, Function = job_function, Title = official_title, Grade = grade, Min = minimum, Mid = midpoint, Max = maximum) %>% 
  filter(Family == input$jfamily,
         Function == input$jfunction),
  options = list(
  columnDefs = list(list(className = 'dt-center', targets = 5)),
  pageLength = 5,
  lengthMenu = c(5, 10, 15, 20)
  )
)
```

Row
-----------------------------------------------------------------------

### Job Function Descriptions

```{r}
htmlOutput("function_description")
output$function_description <- renderUI({
    career_tracks %>% 
  filter(job_family == input$jfamily,
         job_function == input$jfunction) %>% 
    .$job_summary %>% 
    unique()
})
```


### Normal Distribution of Salaries (Hypothetical)

```{r}

jotitle <- eventReactive(input$button, {
    input$jtitle
  })

pdata <- eventReactive(input$button, {
    career_tracks %>% 
      filter(job_family == input$jfamily,
         job_function == input$jfunction,
         official_title == input$jtitle)
})
  
empsal <- eventReactive(input$button, {
    input$emp_salary
})

sal_sd <- eventReactive(input$button, {
  pdata()$midpoint/10
})

emp_perc <- eventReactive(input$button, {
  round(pnorm(empsal(), mean = pdata()$midpoint, sd = sal_sd()) * 100)
})

  
output$plot1 <- renderPlot({
    normal_prob_area_plot(pdata()$midpoint - sal_sd(), 
                          pdata()$midpoint + sal_sd(), 
                          mean = pdata()$midpoint, 
                          sd = sal_sd()) +
    geom_vline(xintercept = pdata()$midpoint, color = "green", linetype = "dashed") +
    geom_vline(xintercept = empsal(), color = "red", linetype = "dashed") +
    scale_x_continuous(labels = scales::dollar) +
    labs(x = "Annual Salary", 
    title = jotitle(), 
    subtitle = paste("Your salary (red line) is at the ", emp_perc(), "th percentile.", sep = "")) +
    theme_ipsum() +
    theme(axis.title.y=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks.y=element_blank()
    )
})

plotOutput("plot1")
```

Other Information
=======================================================================

Row {.tabset}
-----------------------------------------------------------------------

### Levels

```{r}
output$plot2 <- renderPlot({
  career_tracks %>% 
  count(level) %>% 
  ggplot(aes(reorder(level, n), n)) +
  geom_bar(stat = "identity", fill = "darkblue", color = "black") +
  geom_text(stat = "identity", aes(label = n), color = "red", nudge_y = 5) +
  labs(x = "Level",
       y = "Count", 
       title = "UC Career Tracks Levels", 
       subtitle = "Counts of Existing Levels",
       caption = "Source: UCSC Career Tracks Station") +
  coord_flip() +
  theme_ipsum()
})
plotOutput("plot2")
```


### Grades

```{r}
output$plot3 <- renderPlot({
  career_tracks %>% 
  filter(grade != "") %>% 
  count(grade) %>% 
  ggplot(aes(reorder(grade, n), n)) +
  geom_bar(stat = "identity", fill = "yellow", color = "black") +
  geom_text(stat = "identity", aes(label = n), nudge_y = 3, color = "red") +
  labs(x = "Grade",
       y = "Count", 
       title = "UC Career Tracks Grades", 
       subtitle = "Counts of Existing Grades",
       caption = "Source: UCSC Career Tracks Station") +
  coord_flip() +
  theme_ipsum()
})
plotOutput("plot3")
```

### Personnel Program

```{r}
output$plot4 <- renderPlot({
  career_tracks %>% 
  filter(per_prog != "") %>% 
  count(per_prog) %>% 
  ggplot(aes(reorder(per_prog, n), n)) +
  geom_bar(stat = "identity", fill = "lightgreen", color = "black") +
  geom_text(stat = "identity", aes(label = n), color = "red", nudge_y = 35, size = 6) +
  labs(x = "Personnel Program",
       y = "Count", 
       title = "UC Career Tracks Personnel Programs", 
       subtitle = "Counts of Personnel Programs",
       caption = "Source: UCSC Career Tracks Station") +
  theme_ipsum()
})
plotOutput("plot4")
```


